The development of infants' responses to mispronunciations - A Meta-Analysis

### 2018-12-07 Paper_Analyses.Rmd
added an abstract, keywords, and figure captions

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

keywords          : "keywords"
wordcount         : "X"

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf

@@

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line()#,
    #text=element_text(family='Times', size=25)
    )

@@

```{r PRISMA_image, echo= FALSE}

@@

```{r FunnelCombo, echo = FALSE}

@@

```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11}

@@

```{r Vocab_describe1}
#how did vocabulary collection change over time?

@@

```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11}

@@

```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11}

@@

[Christina: Do you want to add this section?]
[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models. But, I am not sure I did it right. I don't really feel like they have to be included, but if you think it would be good, then we can work on it.]

@@

Furthermore, the investigation of mispronunciation sensitivity does not singularly capture infant phono-lexical development. For example, studies investigating word form recognition, typically using the Headturn Preference Procedure (Mandel et al., 1995), allow for an investigation of the specificity of infants' word form representations without requiring word-object associations, which is required in the Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013). As a result, this approach can be used with infants of a much younger age than typically examined. These studies compare infants' preference to listen to word lists that a correct compared to word lists that contain a mispronunciation (e.g. Bouchon et al., 2014; Swingley, 2005; Halle & de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman & Majorano 2016; 2017; Poltrock & Nazzi, 2015; Delle Luche et al., 2016). In contrast, studies investigating recognition of accented words use stimuli that are naturally occuring as opposed to artificially manipulated, to achieve an altered phonological form (e.g. van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014). This allows for an evaluation of phono-lexical development in response to a type of language that infants may encounter in everyday life. These investigations offer complementary approaches to infant phono-lexical development.

>>>>

abstract: |
  As they develop into mature speakers of their native language, infants must not only learn words but also the sounds that make up those words. To do so, they must strike a balance between accepting some variation (e.g. mood, voice, accent), but appropriately rejecting variation when it changes a word's meaning (e.g. cat vs. hat). We focus on studies investigating infants' ability to detect mispronunciations in familiar words, which we refer to as mispronunciation sensitivity. The goal of this meta-analysis was to evaluate the development of mispronunciation sensitivity in infancy, allowing for a test of competing mainstream theoretical frameworks. The results show that although infants are sensitive to mispronunciations, they still accept these altered forms as labels for target objects. Interestingly, this ability is not modulated by age or vocabulary size, challenging existing theories and suggesting that a mature understanding of native language phonology is present in infants from an early age. Despite this finding, we discuss potential data analysis choices that may influence different conclusions about mispronunciation sensitivity development as well as offer recommendations to improve best practices in the study of mispronunciation sensitivity.

keywords          : "language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon"
wordcount         : "X"

@@

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_docx

@@

#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

```{r PRISMA_image, echo= FALSE, fig.cap="A PRISMA flowchart illustrating the selection procedure used to include studies in the current meta-analysis."}

@@

```{r FunnelCombo, echo = FALSE, fig.cap="Funnel plots for object identification, plotting the standard error of the effect size in relation to the effect size. The black line marks zero, the dashed grey line marks the effect estimate, and the grey line marks funnel plot assymetry."}

@@

```{r PlotMPEffect, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivyt (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance)."}

@@

```{r Vocab_describe1, fig.cap="Counts of studies included in the meta-analysis as a function of publication year, representing whether the study did not measure vocabulary (orange), did measure vocabulary and was reported to predict mispronunciation sensitivity (blue), or did measure vocabulary and was reported to not predict mispronunciation sensitivity (green)."}
#how did vocabulary collection change over time?

@@

```{r Plot_post_name_cond_age, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different lengths of post-naming phase time windows analyzed: 2000 ms or less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green). Although length of post-naming phase time window analyzed was included as a continuous variable in the meta-analytic model, it is divided into categories for ease of viewing. Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error."}

@@

```{r Plot_Within_cond_age_diff_score, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Effect sizes for the different types of dependent variables calculated: Post (orange), Post vs. Pre (blue), and Difference Score (green). Panel a plots mispronunciation sensitivity aggregated over age, while panel b plots mispronunciation sensitivity as a function of age. The lines plot the linear regression and the gray shaded area indicates the standard error."}

@@

#[Christina: Do you want to add this section?]
#[Katie: From what I came up with, it makes no difference to the conclusions we make in the regular models. But, I am not sure I did it right. I don't really feel like they have to be included, but if you think it would be good, then we can work on it.]

@@

Furthermore, the investigation of mispronunciation sensitivity does not singularly capture infant phono-lexical development. For example, studies investigating word form recognition, typically using the Headturn Preference Procedure (Mandel et al., 1995), allow for an investigation of the specificity of infants' word form representations without requiring word-object associations, which is required in the Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013). As a result, this approach can be used with infants of a much younger age than typically examined. These studies compare infants' preference to listen to word lists that a correct compared to word lists that contain a mispronunciation (e.g. Bouchon et al., 2014; Swingley, 2005; Halle & de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman & Majorano 2016; 2017; Poltrock & Nazzi, 2015; Delle Luche et al., 2016). In contrast, studies investigating recognition of accented words use stimuli that are naturally occuring as opposed to artificially manipulated, to achieve an altered phonological form (e.g. van Heughten et al., 2018; 2015; Buckler et al., 2017; van Heughten & Johnson, 2014; 2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012; Schmale & Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014; White & Aslin, 2011). This allows for an evaluation of phono-lexical development in response to a type of language that infants may encounter in everyday life. These investigations offer complementary approaches to infant phono-lexical development.

### 2018-12-07 Paper_Analyses.tex
added an abstract, keywords, and figure captions

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
One or two sentences providing a \textbf{basic introduction} to the
field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background},
comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being
addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here
we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals
in direct comparison to what was thought to be the case previously, or
how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general
context}.

Two or three sentences to provide a \textbf{broader perspective},
readily comprehensible to a scientist in any discipline.

@@

\begin{figure}
\centering
\includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Vocab_describe1-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Plot_Within_cond_age_diff_score-1.pdf}
\caption{}
\end{figure}

\subsection{Controlling for analysis
choices}\label{controlling-for-analysis-choices}

{[}Christina: Do you want to add this section?{]}{[}Katie: From what I
came up with, it makes no difference to the conclusions we make in the
regular models. But, I am not sure I did it right. I don't really feel
like they have to be included, but if you think it would be good, then
we can work on it.{]}

@@

Furthermore, the investigation of mispronunciation sensitivity does not
singularly capture infant phono-lexical development. For example,
studies investigating word form recognition, typically using the
Headturn Preference Procedure (Mandel et al., 1995), allow for an
investigation of the specificity of infants' word form representations
without requiring word-object associations, which is required in the
Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
As a result, this approach can be used with infants of a much younger
age than typically examined. These studies compare infants' preference
to listen to word lists that a correct compared to word lists that
contain a mispronunciation (e.g.~Bouchon et al., 2014; Swingley, 2005;
Halle \& de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman \&
Majorano 2016; 2017; Poltrock \& Nazzi, 2015; Delle Luche et al., 2016).
In contrast, studies investigating recognition of accented words use
stimuli that are naturally occuring as opposed to artificially
manipulated, to achieve an altered phonological form (e.g.~van Heughten
et al., 2018; 2015; Buckler et al., 2017; van Heughten \& Johnson, 2014;
2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012;
Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014).
This allows for an evaluation of phono-lexical development in response
to a type of language that infants may encounter in everyday life. These
investigations offer complementary approaches to infant phono-lexical
development.

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
            pdfkeywords={language acquisition; mispronunciation sensitivity; word recognition;
meta-analysis; lexicon},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Hearing and Speech Sciences, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{language acquisition; mispronunciation sensitivity; word recognition; meta-analysis; lexicon\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\abstract{
As they develop into mature speakers of their native language, infants
must not only learn words but also the sounds that make up those words.
To do so, they must strike a balance between accepting some variation
(e.g.~mood, voice, accent), but appropriately rejecting variation when
it changes a word's meaning (e.g.~cat vs.~hat). We focus on studies
investigating infants' ability to detect mispronunciations in familiar
words, which we refer to as mispronunciation sensitivity. The goal of
this meta-analysis was to evaluate the development of mispronunciation
sensitivity in infancy, allowing for a test of competing mainstream
theoretical frameworks. The results show that although infants are
sensitive to mispronunciations, they still accept these altered forms as
labels for target objects. Interestingly, this ability is not modulated
by age or vocabulary size, challenging existing theories and suggesting
that a mature understanding of native language phonology is present in
infants from an early age. Despite this finding, we discuss potential
data analysis choices that may influence different conclusions about
mispronunciation sensitivity development as well as offer
recommendations to improve best practices in the study of
mispronunciation sensitivity.

@@

\begin{figure}
\centering
\includegraphics{figures/Figure_1_PRISMA_MA_Mispronunciation.png}
\caption{(\#fig:PRISMA\_image)A PRISMA flowchart illustrating the
selection procedure used to include studies in the current
meta-analysis.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/FunnelCombo-1.pdf}
\caption{\label{fig:FunnelCombo}Funnel plots for object identification,
plotting the standard error of the effect size in relation to the effect
size. The black line marks zero, the dashed grey line marks the effect
estimate, and the grey line marks funnel plot assymetry.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/PlotMPEffect-1.pdf}
\caption{\label{fig:PlotMPEffect}Panel a: Effect sizes for correct
pronunciations (orange) and mispronunciations (blue) by participant age.
Panel b: Effect sizes for mispronunciation sensitivyt (correct -
mispronunciations) by participant age. For both panels, point size
depicts inverse variance and the dashed line indicates zero (chance).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Vocab_describe1-1.pdf}
\caption{(\#fig:Vocab\_describe1)Counts of studies included in the
meta-analysis as a function of publication year, representing whether
the study did not measure vocabulary (orange), did measure vocabulary
and was reported to predict mispronunciation sensitivity (blue), or did
measure vocabulary and was reported to not predict mispronunciation
sensitivity (green).}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Plot_post_name_cond_age-1.pdf}
\caption{(\#fig:Plot\_post\_name\_cond\_age)Effect sizes for the
different lengths of post-naming phase time windows analyzed: 2000 ms or
less (orange), 2001 to 3000 ms (blue), and 3001 ms or greater (green).
Although length of post-naming phase time window analyzed was included
as a continuous variable in the meta-analytic model, it is divided into
categories for ease of viewing. Panel a plots mispronunciation
sensitivity aggregated over age, while panel b plots mispronunciation
sensitivity as a function of age. The lines plot the linear regression
and the gray shaded area indicates the standard error.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_Analyses_files/figure-latex/Plot_Within_cond_age_diff_score-1.pdf}
\caption{(\#fig:Plot\_Within\_cond\_age\_diff\_score)Effect sizes for
the different types of dependent variables calculated: Post (orange),
Post vs.~Pre (blue), and Difference Score (green). Panel a plots
mispronunciation sensitivity aggregated over age, while panel b plots
mispronunciation sensitivity as a function of age. The lines plot the
linear regression and the gray shaded area indicates the standard
error.}
\end{figure}

@@

Furthermore, the investigation of mispronunciation sensitivity does not
singularly capture infant phono-lexical development. For example,
studies investigating word form recognition, typically using the
Headturn Preference Procedure (Mandel et al., 1995), allow for an
investigation of the specificity of infants' word form representations
without requiring word-object associations, which is required in the
Intermodal Preferential Looking Paradigm (Golinkoff et al., 1987; 2013).
As a result, this approach can be used with infants of a much younger
age than typically examined. These studies compare infants' preference
to listen to word lists that a correct compared to word lists that
contain a mispronunciation (e.g.~Bouchon et al., 2014; Swingley, 2005;
Halle \& de Boysson-Bardies, 1996; Vihman et al., 2004; Vihman \&
Majorano 2016; 2017; Poltrock \& Nazzi, 2015; Delle Luche et al., 2016).
In contrast, studies investigating recognition of accented words use
stimuli that are naturally occuring as opposed to artificially
manipulated, to achieve an altered phonological form (e.g.~van Heughten
et al., 2018; 2015; Buckler et al., 2017; van Heughten \& Johnson, 2014;
2016; Best et al., 2009; Mulak et al., 2013; Schmale et al., 2010; 2012;
Schmale \& Seidel, 2009; Floccia et al., 2012; Durrant et al., 2014;
White \& Aslin, 2011). This allows for an evaluation of phono-lexical
development in response to a type of language that infants may encounter
in everyday life. These investigations offer complementary approaches to
infant phono-lexical development.
